Insert the article title here

### 2020-07-22 tex/results.tex
add results for nature case

@@

>>>>

\section{Rockstuhl replication}

@@

 \section{Ellis replication and validation}

There are two results from this paper that we aim to replicate, and one of them is a comparison
against experimental results which will lead to a validation.

The first result we show is a replication of a result presented in their supplementary 
material FigureS4 {\color{red}(note sure how to cite this, maybe a link)}. We aimed to replicate the 
black curve since the simulation setup is possible to replicate using PyGBe. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$, we identify the the lower frequency mode ($E_{100}$ in Ellis paper)  that is not a 
longitudinal mode. We identify the Longitudinal modes by comparing normal vs 22 deg incidence runs. These
modes due to its nature do not show up in the normal incidence runs. Then, on the 22 deg incidence 
computations we choose the lower wave number mode that it's not a longitudinal mode. The simulations were 
performed for the Long Edge orientation, meaning that the electric field is polarized along the long edge 
of the pillar that is not the height.

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{AR_22_vs_norm.pdf} 
    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
            Normalized by maximum extinction cross section as a function of wave number,
            for a pillar orientation such that the electric field is parallel polarized 
            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
            We present the results for normal incidence and 22 degrees incidence, 
            for different aspect ratios (AR)
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

THIS ARE THE PEAKS OF FIGURE \ref{fig:AR_22_vs_norm} need to find a better way of 
present these numbers.

AR 1 peaks at frequency\\
normal: [ {\color{green}917.73} 934.092 949.604 957.325]\\
22 deg: [ {\color{red}883.926} {\color{green}917.73} 935.052 949.604 957.325]\\

AR 2 peaks at frequency\\
normal: [ {\color{green}903.233} 926.395 944.762 958.242]\\
22 deg: [ {\color{red}896.517} {\color{green}903.233} 926.395 944.762 958.242]\\

AR 3 peaks at frequency\\
normal: [ {\color{green}888.793} 922.552 931.223 948.613 958.242]\\
22 deg: [ {\color{green}888.793} 899.418 922.552 931.223 958.242]\\

AR 4 peaks at frequency\\
normal: [ {\color{green}876.186} 929.32 946.639 958.242]\\
22 deg: [ {\color{green}876.186} 901.281 921.618 929.32 945.745 958.242]\\

AR 5 peaks at frequency\\
normal: [ {\color{green}865.576} 926.395 945.745 958.242]\\
22 deg: [ {\color{green}865.576} 901.281 921.618 958.242]\\

AR 6 peaks at frequency\\
normal: [ {\color{green}856.904} 914.793 923.489 929.32 946.639 958.242]\\
22 deg: [ {\color{green}856.904} 901.281 920.6 958.242]\\

AR 7 peaks at frequency
normal: [ {\color{green}850.134} 910.963 921.618 928.372 946.639 958.242]
22 deg: [ {\color{green}850.134} 901.281 910.963 920.6 958.242]

In other words, we choose the lower mode (lower wavenumber) from the normal 
incidence cases.

Our simulations differ on the method and we do not have a substrate included. The black curve on 
Ellis et al \cite{ellis2016} represents the resonance positions for the $E_{100}$ mode for the different 
aspect ratios when the pillar are separated by a 5000 nm gap. The simulations performed with \pygbe 
consist of one isolated pillar.

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
    \caption{Replication of figure S4 of supplementary material of Ellis 2016}
    \label{fig:rep_FS4_ellis}
 \end{figure}

 If we calculate de relative percentage error for each of these points we get:

 \begin{table}
    \centering
    \caption{\label{table:err_AR} Percentage error for different aspect ratios.} 
    \begin{tabular}{c c}
    \hline%\toprule
    ARR & \% error \\
    \hline%\midrule
     $1$ & $0.95$ \\
     $2$ & $0.67$ \\
     $3$ & $0.35$ \\
     $4$ & $0.16$ \\
     $5$ & $0.72$ \\
     $6$ & $1.20$ \\
     $7$ & $1.59$ \\
    \hline%\bottomrule
    \end{tabular}
\end{table}

\pygbe AR=4 attempt of validation Figure 2a (see Figure \ref{fig:pygbe_vs_exp_2a})

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
    \caption{\pygbe vs experiments, figure 2a of Ellis 2016. Ellis et al 
    has near field interaction in its experiments. Ellis data was digitized
    with web digitizer.}
    \label{fig:pygbe_vs_exp_2a}
 \end{figure}

First order approximation to achieve validation. In our code we do not have near 
field interaction. From Figure S4 in supplementary material of Ellis et al. We know that 
for the first mode ($E_{100}$) the difference between interaction and no interaction is 
12.17 $cm^{-1}$ (obtained from digitized data). If we use this as a first order approximation,
we can subtract that value from our curve, and the results are in Figure \ref{fig:val_2a}

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{validation_FOA_fig2a_Ellis.pdf} 
    \caption{Validation against experiments in figure 2a of Ellis 2016, using first order approximation}
    \label{fig:val_2a}
 \end{figure}

If we use the same approximation and compare the results with Ellis simulations on
Figure 2 of their paper (green curve) we get (see Figure \ref{fig:rep_2a})

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{replication_FOA_fig2a_Ellis.pdf} 
    \caption{Replication of simulations in figure 2a of Ellis 2016, using first
     order approximation}
    \label{fig:rep_2a}
 \end{figure}
